\documentclass[letterpaper,10pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

% Adjust margins for better spacing
\geometry{
  left=0.15in,
  right=0.15in,
  top=0.2in,
  bottom=0.2in
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\normalsize\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Rishabh Sharma}
\end{center}
\begin{center}
    \small
    445-260-7077 $|$
    \href{mailto:rishabh.sharma1103@gmail.com}{\underline{rishabh.sharma1103@gmail.com}} $|$
    \href{https://www.linkedin.com/in/rishabhsharma1104/}{\underline{linkedin.com/in/rishabhsharma1104}} $|$
    \href{https://www.rishabhsharma.co/}{\underline{rishabhsharma.co}} $|$
    \href{https://github.com/ris3abh}{\underline{github.com/ris3abh}} $|$
    Philadelphia, PA
\end{center}

%-----------Professional Summary-----------
\section{PROFESSIONAL SUMMARY}  
Results-driven MLOps Engineer with a Master’s in Data Science, delivering 40\% faster ML deployments via Kubernetes on AWS and 30\% cost savings through cloud optimization. Led cross-functional teams to improve model accuracy by 15\% and mentored engineers, boosting productivity by 20\%. Passionate about fostering innovation, inclusivity, and continuous learning.

%-----------Technical Skills-----------
\section{TECHNICAL SKILLS}
\resumeSubHeadingListStart
\resumeItem{
{\fontsize{9}{11}\selectfont
\begin{tabularx}{\textwidth}{@{} l X @{}}
\textbf{Programming Languages:} & Python, SQL \\
\textbf{Web Frameworks:} & FastAPI, Flask, Django \\
\textbf{Cloud Platforms:} & AWS, Azure, GCP \\
\textbf{Database Technologies:} & MongoDB, PostgreSQL \\
\textbf{Containerization:} & Docker, Kubernetes \\
\textbf{Data Processing \& Analytics:} & Spark (MLlib, Spark SQL), Pandas, Numpy \\
\textbf{CI/CD Pipelines:} & Jenkins, GitLab CI, GitHub Actions \\
\textbf{Infrastructure as Code:} & Terraform, CloudFormation \\
\textbf{Microservices Architecture:} & Design and implementation of cloud-native applications \\
\textbf{Soft Skills:} & Excellent communication, collaboration, problem-solving, attention to detail \\
\end{tabularx}
}
}
\resumeSubHeadingListEnd\section{EXPERIENCE}
\resumeSubHeadingListStart

%-----------Katbotz EXPERIENCE-----------
\resumeSubheading
{Katbotz}{\textit{September 2024 -- Present}}
{Senior Backend Engineer}{New York City, NY}
\resumeItemListStart
    \resumeItem{Designed and deployed Kubernetes clusters on AWS to enhance microservices architecture, containerizing ML models and reducing deployment time by 40\% for scalable applications.}
    \resumeItem{Orchestrated CI/CD pipelines using Jenkins for smooth deployment of RESTful APIs, improving model retraining accuracy by 15\% and cutting downtime by 30\%.}
    \resumeItem{Collaborated with cross-functional teams to implement FastAPI for API development, ensuring production-ready endpoints met performance optimization requirements.}
    \resumeItem{Developed feature engineering pipelines on Spark for real-time analytics, accelerating data preprocessing by 40\% and maintaining strong attention to detail.}
    \resumeItem{Mentored 3 junior engineers on backend development best practices, fostering collaboration and enhancing team productivity by 20\% through knowledge-sharing initiatives.}
\resumeItemListEnd

%-----------Dark Matter Technologies EXPERIENCE-----------
\resumeSubheading
{Dark Matter Technologies}{\textit{June 2023 -- December 2023}}
{Backend Engineer}{Jacksonville, FL}
\resumeItemListStart
    \resumeItem{Optimized Azure Databricks workflows and RESTful API integrations using Terraform, reducing cloud costs by 25\% and maintaining 99.5\% uptime for backend services.}
    \resumeItem{Streamlined model lifecycle management with AWS SageMaker, reducing retraining cycles from 12 to 4 hours while applying test-driven development principles to boost ROI by 22\%.}
    \resumeItem{Implemented Docker containers for backend services, enabling efficient edge processing and reducing latency by 35\% in distributed cloud-native applications.}
    \resumeItem{Championed Agile Scrum practices, leading a diverse team of 5 to deliver 8 scalable applications in 6 sprints, aligning project outcomes with business goals.}
    \resumeItem{Developed performance dashboards using Tableau, translating backend service efficacy into actionable insights to inform decisions for \$500K infrastructure upgrades.}
\resumeItemListEnd

%-----------Digital Pass EXPERIENCE-----------
\resumeSubheading
{Digital Pass}{\textit{June 2020 -- June 2022}}
{Backend Engineer}{Indore, India}
\resumeItemListStart
    \resumeItem{Engineered GCP-based backend pipelines to automate capacity planning, achieving 30\% cost savings via predictive resource allocation integrated with RESTful APIs.}
    \resumeItem{Transformed raw IoT data into actionable insights using Python, reducing packet loss by 21\% for 2M+ devices through improved backend analytics.}
    \resumeItem{Implemented feature engineering pipelines for machine learning models, improving churn prediction accuracy by 25\% (AUC-ROC: 0.92) with a focus on database technologies.}
    \resumeItem{Collaborated with DevOps to deploy robust monitoring tools within the microservices architecture, cutting incident response time by 40\% through real-time incident detection.}
    \resumeItem{Led training sessions on FastAPI for developing scalable APIs, fostering a culture of continuous learning in cloud-native application development.}
\resumeItemListEnd

%-----------SK Enterprises EXPERIENCE-----------
\resumeSubheading
{SK Enterprises}{\textit{January 2019 -- June 2020}}
{Data Scientist}{Indore, India}
\resumeItemListStart
    \resumeItem{Maximized data utility via PySpark pipelines, cleaning 10TB+ daily customer data to drive 9\% ARPU growth through targeted offerings and data-driven decision-making.}
    \resumeItem{Formulated segmentation models to inform personalized service plans that increased customer retention by 12\%, utilizing problem-solving skills to address customer needs effectively.}
\resumeItemListEnd

\resumeSubHeadingListEnd\section{CERTIFICATIONS}
\resumeSubHeadingListStart
    \resumeItem{AWS Certified Data Engineer Associate (DEA-C01)\hfill \textit{April 2024 -- April 2027}}
\resumeSubHeadingListEnd

%-----------Education-----------
\section{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading
      {Drexel University}{\textit{Philadelphia, PA}}
      {Master of Science in Data Science}{}
    \resumeSubheading
      {Rajiv Gandhi Proudyogiki Vishwavidyalaya}{\textit{Bhopal, India}}
      {Bachelor of Technology in Computer Science and Engineering}{}
\resumeSubHeadingListEnd

\end{document}