\documentclass[letterpaper,10pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge Alex Johnson} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:alex.johnson@email.com}{alex.johnson@email.com} $|$ 
    \href{https://linkedin.com/in/alexjohnson}{linkedin.com/in/alexjohnson} $|$
    San Francisco, CA
\end{center}

% Summary
\section{Summary}
Software engineer with 5 years of experience developing web applications and services. Proficient in Python and JavaScript with a focus on building scalable backend systems.

% Experience
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{TechCorp Inc.}{San Francisco, CA}
{Senior Software Engineer}{January 2020 - Present}
\resumeItemListStart
\resumeItem{Backend Development}{Designed and implemented RESTful APIs using Django for an e-commerce platform that processes 10,000+ daily transactions.}
\resumeItem{Database Management}{Optimized PostgreSQL database queries, reducing response time by 40\%.}
\resumeItem{Team Leadership}{Led a team of 4 developers in the redesign of the payment processing system.}
\resumeItemListEnd

\resumeSubheading
{DataSystems LLC}{Oakland, CA}
{Software Engineer}{June 2017 - December 2019}
\resumeItemListStart
\resumeItem{Full Stack Development}{Built responsive web applications using React.js and Node.js.}
\resumeItem{Cloud Infrastructure}{Deployed and maintained applications on AWS using Docker containers.}
\resumeItem{Agile Methodology}{Participated in daily stand-ups and biweekly sprint planning.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% Skills
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Python, JavaScript, HTML/CSS, SQL}
\resumeSubItem{Frameworks \& Libraries}{Django, Flask, React.js, Node.js, Express.js}
\resumeSubItem{Tools \& Platforms}{Git, Docker, AWS, Heroku, PostgreSQL, MongoDB}
\resumeSubItem{Methodologies}{Agile Development, Test-Driven Development, CI/CD}
\resumeSubHeadingListEnd

% Education
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of California, Berkeley}{Berkeley, CA}
{Bachelor of Science in Computer Science}{August 2013 - May 2017}
\resumeSubHeadingListEnd

\end{document}